---
title       : Diamond Price Predictor
subtitle    : by carat
author      : Xiu Ren Yap
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Aim

This app makes a quick estimate of the price of a diamond based on the carat,
so that one can make an informed choice before buying or selling a diamond.

--- .class #id 

## Method

In our app, we use a linear model to fit through the data from the dataset of diamonds.
Therefore, the prediction is but a very rough estimate.

```{r model, echo = TRUE, warning=FALSE, message=FALSE}
library(ggplot2)
data(diamonds)
modelFit <- lm(price ~ carat, data = diamonds)
```

--- .class #id 
## Output

From the model fit shown on the slide before, we estimate the price as below.
Let's look at an example where user enters 2 carat.

```{r priceEst, echo=TRUE}
carat <- 2
perCarat <- coef(modelFit)[2]
intercept <- modelFit$coefficients[1]
totalPrice <- as.numeric(intercept + carat * perCarat)
totalPrice
```

where carat is the value obtained from the input from user.

--- .class #id 
## Further improvements in future versions

- Future version of the app will include multivariate regression models.
- This will result in better accuracy.



